---
title: "Assignment6"
author: "Rebecca Larsen"
format: html
editor: visual
---

## Lab LinearRegression01

by Dr. Karl Ho

#### Load Libraries

```{r}
# install and load pacman for package management
if (!require("pacman", character.only = TRUE)) install.packages("pacman")
library(pacman)
# load libraries using pacman
p_load("easypackages","MASS","ISLR","arm","rtweet","tidyverse","RColorBrewer","tidytext","data.table","tidyr","coefplot2")

```

#### Load Data

```{r}
## Load datasets from MASS and ISLR packages
attach(Boston)
```

#### Simple Linear Regression and Dataset Exploration

```{r}
### Simple linear regression
names(Boston)
# What is the Boston dataset?
?Boston
plot(medv~lstat,Boston, pch=20, cex=.8, col="steelblue")
fit1=lm(medv~lstat,data=Boston)
fit1
summary(fit1)
abline(fit1,col="firebrick")
names(fit1)
confint(fit1) # confidence intervals

# Predictions using values in lstat
predict(fit1,data.frame(lstat=c(0,5,10,15)),interval="confidence") # confidence intervals
predict(fit1,data.frame(lstat=c(0,5,10,15)),interval="prediction") # prediction intervals

# Prediction interval uses sample mean and takes into account the variability of the estimators for μ and σ.
# Therefore, the interval will be wider.
```

#### Multiple Linear Regression

```{r}
### Multiple linear regression
fit2=lm(medv~lstat+age,data=Boston)
summary(fit2)
fit3=lm(medv~.,Boston)
summary(fit3)
par(mfrow=c(2,2))
plot(fit3,pch=20, cex=.8, col="steelblue")
mtext("fit3", side = 3, line = - 2, cex = 2, outer = TRUE)

# Update function to re-specify the model, i.e. include all but age and indus variables
fit4=update(fit3,~.-age-indus)
summary(fit4)

# Set the next plot configuration
par(mfrow=c(2,2), main="fit4")
plot(fit4,pch=20, cex=.8, col="steelblue")
mtext("fit4", side = 3, line = - 2, cex = 2, outer = TRUE)

# Uses coefplot to plot coefficients.  Note the line at 0.
par(mfrow=c(1,1))
arm::coefplot(fit4)

### Nonlinear terms and Interactions
fit5=lm(medv~lstat*age,Boston) # include both variables and the interaction term x1:x2
summary(fit5)

## I() identity function for squared term to interpret as-is
## Combine two command lines with semicolon
fit6=lm(medv~lstat +I(lstat^2),Boston); summary(fit6)
par(mfrow=c(1,1))
plot(medv~lstat, pch=20, col="forestgreen")

points(lstat,fitted(fit6),col="firebrick",pch=20)
fit7=lm(medv~poly(lstat,4))
points(lstat,fitted(fit7),col="steelblue",pch=20)


```

#### Qualitative Predictors

```{r}
###Qualitative predictors
names(Carseats)
summary(Carseats)
fit1=lm(Sales~.+Income:Advertising+Age:Price,Carseats) # add two interaction terms
summary(fit1)
attach(Carseats)
contrasts(Carseats$ShelveLoc) # what is contrasts function?
?contrasts

```

#### Write an R function to combine lm, plot, & abline functions

```{r}
### Writing an R function to combine the lm, plot and abline functions to 
### create a one step regression fit plot function
regplot=function(x,y){
  fit=lm(y~x)
  plot(x,y, pch=20)
  abline(fit,col="firebrick")
}
attach(Carseats)
regplot(Price,Sales)
## Allow extra room for additional arguments/specifications
regplot=function(x,y,...){
  fit=lm(y~x)
  plot(x,y,...)
  abline(fit,col="firebrick")
}
regplot(Price,Sales,xlab="Price",ylab="Sales",col="steelblue",pch=20)

```

#### Next Steps

```{r}
## Additional note: try out the coefplot2 package to finetune the coefplots
install.packages("coefplot2", repos="http://www.math.mcmaster.ca/bolker/R", type="source")
library(coefplot2)

# Exercise 
# Try other combination of interactive terms
names(Carseats)
summary(Carseats)
fit2=lm(Sales~.+Education:Age+Urban:Income, Carseats) # add another interaction term
summary(fit2)
attach(Carseats)
contrasts(Carseats$ShelveLoc) # what is contrasts function?
?contrasts
# How to interpret interactive terms?

# Read: Brambor, T., Clark, W.R. and Golder, M., 2006. Understanding interaction models: Improving empirical analyses. Political analysis, 14(1), pp.63-82.

```

**Question:** How to interpret interactive terms?

Answer: According to Brombor et al. (2006), "an increase in X is associated with an increase in Y when condition Z is met, but not when condition Z is absent." Interaction terms are used to set up conditional hypotheses. In our above model, when in an urban area, income has a negative impact on carseats.

**Question:** What are qualitative variables? What class should they be?

Answer: Qualitative variables are categorical variables. They can be at the ordinal or nominal level of measurement. Particularly for nominal and two-class nominal variables (dichotomous), linear model assumptions are not met if they are used as dependent variables. This requires analysis that can explore the impact a difference in category has as there is no increase in category, only a change. Some linear regression models can be used when categorical variables are independent variables, because we are looking at comparison groups. For example, compared to whatever the base category is, when observe the slope change on the dependent variable. These can also work well for interaction terms. When an area is urban, then education's impact on car seat sales is different than it is on its own.
