---
title: "Assignment03"
author: "Rebecca Larsen"
date: "2023-02-22"
output: html_document
---

# Lab 3 

# R Programming (EDA)

(Adapted from Stackoverflow examples) (Objectives: Use plotly, reshape packages, interactive visualization)

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
data(iris)
attach(iris)
# Generate plot on three quantitative variables
iris_plot <- plot_ly(iris,
                     x = Sepal.Length,
                     y = Sepal.Width,
                     z = Petal.Length,
                     type = "scatter3d",
                     mode = "markers",
                     size = 0.02)
iris_plot
# Regression object

petal_lm <- lm(Petal.Length ~ 0 + Sepal.Length + Sepal.Width,
               data = iris)
library(reshape2)

#load data

petal_lm <- lm(Petal.Length ~ 0 + Sepal.Length + Sepal.Width,data = iris)

# Setting resolution parameter
graph_reso <- 0.05

#Setup Axis
axis_x <- seq(min(iris$Sepal.Length), max(iris$Sepal.Length), by = graph_reso)
axis_y <- seq(min(iris$Sepal.Width), max(iris$Sepal.Width), by = graph_reso)

# Regression surface
# Rearranging data for plotting
petal_lm_surface <- expand.grid(Sepal.Length = axis_x,Sepal.Width = axis_y,KEEP.OUT.ATTRS = F)
petal_lm_surface$Petal.Length <- predict.lm(petal_lm, newdata = petal_lm_surface)
petal_lm_surface <- acast(petal_lm_surface, Sepal.Width ~ Sepal.Length, value.var = "Petal.Length")
hcolors=c("orange","blue","green")[iris$Species]
iris_plot <- plot_ly(iris,
                     x = ~Sepal.Length,
                     y = ~Sepal.Width,
                     z = ~Petal.Length,
                     text = Species,
                     type = "scatter3d",
                     mode = "markers",
                     marker = list(color = hcolors),
                     size=0.02)
# Add surface
iris_plot <- add_trace(p = iris_plot,
                       z = petal_lm_surface,
                       x = axis_x,
                       y = axis_y,
                       type = "surface",mode = "markers",
                       marker = list(color = hcolors))
iris_plot
```

# Regression object

```{r}
petal_lm <- lm(Petal.Length ~ 0 + Sepal.Length + Sepal.Width, 
               data = iris)
```

# Assignment 3 

```{r}
library(haven) 
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

```{r}
## New Dataset with NDIR and Tax as ordinal variable##
myvars <- c("Tondu", "female", "DPP", "age", "income", "edu", "Taiwanese", "Econ_worse")
newdata <- TEDS_2016[myvars]
```

```{r}
newdata$Tondu<-as.numeric(newdata$Tondu,labels=c("Unification now”, “Status quo, unif. in future”, “Status quo, decide later", "Status quo forever", "Status quo, indep. in future", "Independence now”, “No response"))
```

```{r}
model1=lm(Tondu~age+edu+income,
data=newdata) 
summary(model1)
plot(model1)

```

Q: What is the problem? Why? A: The DV is a 7-category nominal variable. A linear regression model does not work to predict a variable that is not numeric, but especially when the scale does not have a meaningful order and consistent spacing.The variable we are trying to predict is likely not linear.

Q: What can be done to improve prediction of the dependent variable? A: A logit regression could help with prediction, but that is still assuming model fit without testing for it. More important is to find a model that fits the data.Testing multiple model's ROC curves could help with prediction of the dependent variable.
